---
title: "Table outputs for paper"
author: "Andy Baxter"
date: "16/03/2022"
output: 
  word_document:
    reference_docx: template.docx
---

```{r setup, include=TRUE, message=FALSE, results='hide', echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(gt)
source("../R/import and convert.R")
source("../R/functions.R")
source("../R/tables_functions.R")
library(tidyverse)
```

# Table 1 — Socio-demographic characteristics of sexually active participants aged 18-44 years, described as female at birth who reported sex with a man in the past year

```{r}
wave2_data %>%
  mutate(
    D_Edu3Cat_w2 = fct_rev(D_Edu3Cat_w2),
    SDSdrinkchangeW2_w2 = fct_rev(SDSdrinkchangeW2_w2)
  ) %>%
  demographics_per_outcome(
    D_Age5Cat_w2,
    Total,
    D_EthnicityCombined_w2,
    D_SexIDL_w2,
    qsg,
    D_Edu3Cat_w2,
    D_relstatcatv7_w2,
    EconActChg4_w2,
    EconActChg5_w2,
    D_drinkGrp_w2,
    SDSdrinkchangeW2_w2,
    Smokenow_w2,
    D_PHQ2Cat_w2,
    D_GAD2Cat_w2
  )
```


# Table 2 — Contraception used in the year since the start of the first UK lockdown by participants aged 18-44 years who were sexually active and were not pregnant, not trying to get pregnant or not unable to get pregnant

```{r}
wave2_data %>%
  filter(as.numeric(D_ConNoCon_w2) != 4) %>% 
  mutate(across(where(is.factor), .fns = ~fct_drop(.x)),
           D_Edu3Cat_w2 = fct_rev(D_Edu3Cat_w2),
           SDSdrinkchangeW2_w2 = fct_rev(SDSdrinkchangeW2_w2)
         ) %>% 
  crosstab_per_outcome(
    D_ConNoCon_w2,
    Total,
    D_Age5Cat_w2,
    D_EthnicityCombined_w2,
    D_SexIDL_w2,
    qsg,
    D_Edu3Cat_w2,
    D_relstatcatv7_w2,
    EconActChg4_w2,
    EconActChg5_w2,
    D_drinkGrp_w2,
    SDSdrinkchangeW2_w2,
    Smokenow_w2,
    D_PHQ2Cat_w2,
    D_GAD2Cat_w2
  )  
```

# Table 3 — Whether users of ‘more effective’ contraceptives pre-lockdown switched from usual contraception method pre-Covid, among participants who were not pregnant, not trying to get pregnant and not unable to get pregnant
```{r}
wave2_data %>%
  filter(as.numeric(D_ConNoCon_w2) != 4,
         D_ConPreUs_w2 == "More effective method") %>%
  mutate(
    across(where(is.factor), .fns = ~ fct_drop(.x)),
    D_Edu3Cat_w2 = fct_rev(D_Edu3Cat_w2),
    SDSdrinkchangeW2_w2 = fct_rev(SDSdrinkchangeW2_w2),
    D_StopOrSwitch_w2 = fct_collapse(
      D_SwitchTo_w2,
      "Stopped using contraceptives" = "Stopped using contraceptives",
      "Did not switch or stop usual method" = "Did not switch or stop usual method",
      other_level = "Switched usual or only contraceptive method"
    ) %>%
      fct_relevel(
      "Did not switch or stop usual method",
      "Stopped using contraceptives",
      "Switched usual or only contraceptive method"
      ),
    D_SwitchTo_w2 = fct_rev(D_SwitchTo_w2)
  ) %>% 
  crosstab_per_outcome(
    D_SwitchTo_w2,
    Total,
    D_Age5Cat_w2,
    D_EthnicityCombined_w2,
    D_SexIDL_w2,
    qsg,
    D_Edu3Cat_w2,
    D_relstatcatv7_w2,
    EconActChg4_w2,
    EconActChg5_w2,
    D_drinkGrp_w2,
    SDSdrinkchangeW2_w2,
    Smokenow_w2,
    D_PHQ2Cat_w2,
    D_GAD2Cat_w2
  )
```



# Table S1

```{r}
wave2_data %>%
  filter(as.numeric(D_ConServAcc_w2) != 1) %>% 
  mutate(across(where(is.factor), .fns = ~fct_drop(.x)),
         D_Edu3Cat_w2 = fct_rev(D_Edu3Cat_w2),
         SDSdrinkchangeW2_w2 = fct_rev(SDSdrinkchangeW2_w2)
  ) %>% 
  crosstab_per_outcome(
    D_ConServAcc_w2,
    Total,
    D_Age5Cat_w2,
    D_EthnicityCombined_w2,
    D_SexIDL_w2,
    qsg,
    D_Edu3Cat_w2,
    D_relstatcatv7_w2,
    EconActChg4_w2,
    EconActChg5_w2,
    D_drinkGrp_w2,
    SDSdrinkchangeW2_w2,
    Smokenow_w2,
    D_PHQ2Cat_w2,
    D_GAD2Cat_w2
  )

```

# Table S3

```{r}
wave2_data %>%
  filter(as.numeric(D_ConNoCon_w2) != 4,
         as.numeric(D_ConPre_w2) != 3) %>% 
  mutate(across(where(is.factor), .fns = ~fct_drop(.x)),
         D_Edu3Cat_w2 = fct_rev(D_Edu3Cat_w2),
         SDSdrinkchangeW2_w2 = fct_rev(SDSdrinkchangeW2_w2)
  ) %>% 
  crosstab_per_outcome(
    D_SwitchTo_w2,
    Total,
    D_Age5Cat_w2,
    D_EthnicityCombined_w2,
    D_SexIDL_w2,
    qsg,
    D_Edu3Cat_w2,
    D_relstatcatv7_w2,
    EconActChg4_w2,
    EconActChg5_w2,
    D_drinkGrp_w2,
    SDSdrinkchangeW2_w2,
    Smokenow_w2,
    D_PHQ2Cat_w2,
    D_GAD2Cat_w2
  )
```

